A Survey on Ordered Binary Decision Diagrams

### 2015-09-15 paper.tex
Revise Apply

\noindent
Using this function, one check if $f_1$ and $f_2$ are functionally equivalent by
computing $(f_1\overline{\oplus}f_2)\lor d$. If the result is \textbf{1}, $f_1$
and $f_2$ are functionally equivalent.

@@

\textit{Shannon's expansion} forms the basis of the recursive
algorithm~\cite{BRYANT86}:
\begin{center}
$
f_1 op f_2 =
\overline{x_i} \cdot \left(f_1|_{x_i\leftarrow 0}\;op\;f_2|_{x_i\leftarrow 0}\right)
+ x_i \cdot \left(f_1|_{x_i\leftarrow 1}\;op\;f_2|_{x_i\leftarrow 1}\right)
$
\end{center}

\noindent
The recursive procedure then has three different cases. Note that a node is only
created if no equivalent node is already present in the resultant graph.
\begin{enumerate}
    \item{
        If $n_1$ and $n_2$ are both terminal nodes, then a terminal node
        representing the value $value(n_1)\;op\;value(n_2)$ is added to the
        resultant graph and the recursion terminates.
    }
    \item{
        If either $n_1$ or $n_2$ is a nonterminal node, then:
        \begin{enumerate}
            \item{
                If $var(n_1) = var(n_2)$, a node having $var(n_1)$ is created and
                the procedure is applied recursively on $(lo(n_1), lo(n_2))$ and
                $(hi(n_1), hi(n_2))$.
            }
            \item{
                If $var(n_1)$ is a nonterminal and $n_2$ is eiter a terminal node
                or $var(n_1) < var(n_2)$, a node having $var(n_1)$ is created and
                the procedure is applied recursively on $(lo(n_1), n_2)$ and
                $(hi(n_1), n_2)$.
            }
        \end{enumerate}
    }
\end{enumerate}

To get a reduced graph immediately, the three transformation rules are utilized
again for each step~\cite{BRYANT92}.

@@

The full pseudocode defined by Bryant can be found in~\cite[p. 685]{BRYANT86}. \tbr

>>>>

\noindent
Using this function, one checks whether $f_1$ and $f_2$ are functionally
equivalent by computing $(f_1\overline{\oplus}f_2)\lor d$. If the result is
\textbf{1}, $f_1$ and $f_2$ are functionally equivalent.

@@

\textit{Shannon's expansion} forms the basis of the recursive
algorithm~\cite{BRYANT86}:
\begin{center}
$
f_1\;op\;f_2 =
\overline{x_i} \cdot \left(f_1|_{x_i=0}\;op\;f_2|_{x_i=0}\right)
+ x_i \cdot \left(f_1|_{x_i=1}\;op\;f_2|_{x_i=1}\right)
$
\end{center}

\noindent
The recursive procedure then has three different cases. Note that a node is only
created if no equivalent node is already present in the resultant graph.
\begin{enumerate}
    \item{
        If $n_1$ and $n_2$ are both terminal nodes, then a terminal node
        representing the value $value(n_1)\;op\;value(n_2)$ is added to the
        resultant graph and the recursion terminates.
    }
    \item{
        If either $n_1$ or $n_2$ is a nonterminal node, then:
        \begin{enumerate}
            \item{
                If $var(n_1) = var(n_2)$, a node having $var(n_1)$ is created and
                the procedure is applied recursively to $(lo(n_1), lo(n_2))$ and
                $(hi(n_1), hi(n_2))$.
            }
            \item{
                If $var(n_1)$ is a nonterminal and $n_2$ is either a terminal node
                or $var(n_1) < var(n_2)$, a node having $var(n_1)$ is created and
                the procedure is applied recursively to $(lo(n_1), n_2)$ and
                $(hi(n_1), n_2)$.
            }
        \end{enumerate}
    }
\end{enumerate}

To get a reduced graph immediately, the three transformation rules are applied
again in each step~\cite{BRYANT92}.

@@

The full pseudocode defined by Bryant can be found in~\cite[p. 685]{BRYANT86}.
